---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fitAQ

<!-- badges: start -->
<!-- badges: end -->

The **fitAQ** package fits four light response models using differential evolution (`DEoptim`).
Models: rectangular hyperbola, non‑rectangular hyperbola, exponential, modified rectangular hyperbola.

Key outputs: LCP, LSP, Pmax, AQY, Rd.

## Installation

```r
# install.packages("devtools")
devtools::install_github("yourusername/fitAQ")
```

## Example with `dat-aq-wait30.csv`

```{r}
library(fitAQ)

# Path to example data
f <- system.file("extdata", "dat-aq-wait30.csv", package = "fitAQ")
df <- read.csv(f)

head(df)
```

Fit exponential model:

```{r}
fit_exp <- fit_light_response(df, Qin = "Qin", A = "A", model = "exponential")
print(fit_exp)
```

Extract parameters:

```{r}
light_points(fit_exp)
```

Compare all four models:

```{r}
models <- c("rectangular", "nonrectangular", "exponential", "modified")
res_list <- lapply(models, function(m) {
  fit_light_response(df, Qin = "Qin", A = "A", model = m)
})
names(res_list) <- models

sapply(res_list, function(x) round(x$value, 2))
```

## Example with `lrc.csv`

```{r}
df2 <- read.csv(system.file("extdata", "lrc.csv", package = "fitAQ"))
names(df2)[names(df2) == "Qin"] <- "PARi"
names(df2)[names(df2) == "A"]   <- "Photo"

fit_rect <- fit_light_response(df2, Qin = "PARi", A = "Photo", model = "rectangular")
light_points(fit_rect)
```

## Model formulas

- Rectangular: \( A = \frac{\alpha Q A_m}{\alpha Q + A_m} - R_d \)
- Non‑rectangular: \( A = \frac{1}{2\theta}\left(\alpha Q + A_m - \sqrt{(\alpha Q + A_m)^2 - 4\alpha\theta A_m Q}\right) - R_d \)
- Exponential: \( A = A_m \left[1 - \exp(-b(Q - I_c))\right] \)
- Modified: \( A = \alpha \frac{1-\beta Q}{1+\gamma Q} Q - R_d \)

## License

MIT © Jiedong Zhu

## References

Baly, EC. 1935. 《The kinetics of photosynthesis》. Proceedings of the Royal Society of London Series B (Biological Sciences), 期 117: 218–39.
Thornley, J H M. 1976. 《Mathematical models in plant physiology》. London: Academic Press.
Prado, C. H., 和 J. A. P. V. De Moraes. 1997. 《Photosynthetic capacity and specific leaf mass in twenty woody species of Cerrado vegetation under field conditions》. Photosynthetica 33 (1): 103–12.
ZiPiao, YE. 2010. 《A review on modeling of responses of photosynthesis to light and CO2CO2​》. Chinese Journal of Plant Ecology, 期 06.
